\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[brazil]{babel}
\usepackage{amsmath,amsthm,amsfonts,stmaryrd,amssymb} % Math packages

\title{Propz Test}
\author{Giovana Vieira de Morais}

\begin{document}
\maketitle

\begin{enumerate}
  \item[Question 2.]{
    Some assumptions I made so I could solve this exercise:
    \begin{itemize}
      \item{1. All elements are integers. This is not explicit said and I
        based this only on the options given;}
      \item{2. The set can be of any possible size. Different sets can lead to
        the same mean and the size is also not given;}
      \item{3. At least 4 of the possible options should be in the set.}
    \end{itemize}
    Ok, given this, my answer is option A) 30.
    First of all, the only rule explicit in the question is that
		$$ x_{max} = 5 + 2*x_{min} $$
		So, if $x_{min} = 30$, $x_{max} = 90$ and all other options greater than
    $x_{max}$ would be outside the set.
    From 50 on, it's possible to find a set with all the options and mean = 100
    for example [50,70,71,70,120,154,155], where $x_{min} = 50$ and
    $x_{max} = 155$, statisfying the $x_{max} = 5 + 3*x_{min}$ condition.
  }

  \item[Question 4]{
    Considering that the costumers buy ONLY in the store of the mentioned
    probability (this is not explicit in the question), we have
    50\% buying in A, 30\% buying in B and 20\% buying in C

    \begin{description}
      \item[a.]{
        for A store, the answer rate is 50\%. so 50\% of the costumers
        did not answer. So here we have 50\% (not-answering-rate) of 50\%
        (costumer that buy at A) and we can manage to find our
        $$ P(didn't answer|A) = 0.5*0.5 = 0.25 $$
        using the same technique, we have
        $$P(didn't answer|B) = 0.4*0.3 = 0.12$$
        and $$P(didn't answer|C) = 0.1*0.2 = 0.02$$

        Now, knowing the "didn't aswer rate" of all three stores, we can
        know too the general rate by summing them: 0.25 + 0.12 + 0.02 = 0.39
        or 39\%. So this is the probability that a random customer didn't
        answer the campaign.
        $$P(didn't answer) = 0.39$$
      }
      \item[b.]{
        To find out a responder that went to C, we can apply Bayes
        \begin{align*}
          P(C|answered) &= \frac{P(answered|C) \cdot P(C)}{P(answered)} \\
                        &= \frac{0.9 \cdot 0.2}{0.61} \\
                        &= 0.2951
        \end{align*}
        So the probability is 29.51\%
    }
    \end{description}
  }

  \item[Question 5]{
    The probability of getting one the b type dice $(P(b))$ is 3/12 and the
    probability of getting a six is 0.85, so the conditional probability is of
    0.2125 or 21.25\%
  }
\end{enumerate}

\end{document}
